`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Finalize a first intro draft (missing citations);

>>>>

Following work by X <CITE>, Y<CITE> and Z<CITE>, we have develloped an assay 
suited to characterize scramblase activity in purified proteins and protein 
extracts <CITE OPSIN PAPER, MIKE, BIRGIT>, based on the reconstitution of 
scramblases or candidate proteins into large synthetic vesicles with a lipid
composition that includes the fluorescent lipid XYC. Upon exposure of these 
vesicles to membrane-impermeable reducing agents such as dithionite, 
fluorophores in the external sheet of the vesicles are quenched and fluorescence
in scramblase-free vesicles accordingly quickly drops to approximately 50% of 
the initial value. However, for vesicles reconstituted with proteins conferring 
a scramblase activity, fluorescence dissapears entirely, as fast 
scramblase-mediated equilibration between outer (exposed) and inner (protected)
sheet of the vesicle membrane renders all fluorescent lipids accessible to 
reduction. By titration of the protein amount reconstituted into the vesicle 
membranes it is thus possible to characterize scramblases and probe their 
activity. Beyond functional validation of candidate scramblases 
<CITE OPSIN, Birgit>, the assay has for example also been used to characterize 
the stoichiometry of scramblase homo-multimers reconstituting into the vesicles
<CITE BIRGIT>.

From the identification of baseline and post-reduction fluorescense from 
fluorometer-generated spectra, via the calculation of the underlying statistics
and through publication-grade representation of the results, data analysis in 
the context of this assay has until now involved an extensive series of manual 
steps, at most supported by spread sheet calculation facilities. Based on the
`R` free software environment for statistical computing and graphics <CITE CORE>
and prominently drawing on the power and elegance of the `ggplot2` plotting 
system <CITE the book>, we here provide `flippant` a comprehensive package
covering fast, reproducible data analysis and graphing for scramblase assays 
from raw fluorescense spectra with a simple parametrizing spreadsheet as the
sole required input.
